---
output: 
  rmarkdown::html_vignette:
    keep_md: true
md_document:
  variant: markdown_github
  
params:
  NVIpkg: "NVIpackage"
title: "Contribute to `r params$NVIpkg`"

vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{`r paste("Contribute to", params$NVIpkg)`}
  %\VignetteEncoding
  
---


```{r, include = FALSE}
NVIpkg <- params$NVIpkg
NVIpkg_inline <- paste0("`", NVIpkg, "`")
NVIpkg_code <- "/tree/main/R"
# pkg_name <- NVIpkg_inline
# pkg_name <- "`NVIcheckmate`"
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

Thank you for considering contributing to `r NVIpkg_inline`. 

`r NVIpkg_inline` is one of several packages assembled under the name `NVIverse`, a collection of R-packages with tools to facilitate data management and data reporting at the Norwegian Veterinary Institute (NVI). 

###  NVIverse packages
```{r echo = FALSE, resuls = 'asis'}
NVIverse <- as.data.frame(rbind(c("NVIconfig", "Private",
                                  "Configuration information necessary for some NVIverse functions"),
                                c("NVIdb", "Public",
                                  "Tools to facilitate the use of NVI's databases"),
                                c("NVIpretty",  "Public",
                                  "Tools to make R-output pretty in accord with NVI's graphical profile"),
                                c("NVIbatch",  "Public",
                                  "Tools to facilitate the running of R-scripts in batch mode at NVI"),
                                c("NVIcheckmate",  "Public",
                                  "Extension of checkmate with additional functions for argument checking for use in NVIverse functions"),
                                c("OKplan",  "Public",
                                  "Tools to facilitate the planning of surveillance programmes for the NFSA"),
                                c("OKcheck",  "Public",
                                  "Tools to facilitate checking of data from national surveillance programmes")))
colnames(NVIverse) <- c("Package", "Status", "Description")
knitr::kable(x = NVIverse)
```
  
## How you can contribute
There are several ways you can contribute to this project: ask a question, propose an idea, report a bug, improve the documentation, or contribute code. 

### Ask a question

Using `r NVIpkg_inline` and need help? Browse the package help to see if you can find a solution. Still problems? Post your question in R-forum at workplace or contact the package maintainer by [email](mailto:petter.hopp@vetinst.no).

### Propose an idea 

Have an idea for a new `r NVIpkg_inline` feature? Take a look at the `r NVIpkg_inline` help and `r paste0("[issue list](https://github.com/NorwegianVeterinaryInstitute/",NVIpkg, "/issues)")` to see if it isn't included or suggested yet. If not, suggest your idea as an `r paste0("[issue on GitHub](https://github.com/NorwegianVeterinaryInstitute/",NVIpkg, "/issues/new)")`. While we can't promise to implement your idea, it helps to:

* Explain in detail how it would work.
* Keep the scope as narrow as possible.

See below if you want to contribute code for your idea as well.

### Report a bug 

Using `r NVIpkg_inline` and discovered a bug? Don't let others have the same experience and report it as an `r paste0("[issue on GitHub](https://github.com/NorwegianVeterinaryInstitute/",NVIpkg, "/issues/new)")` so we can fix it. A good bug report makes it easier for us to do so, so please include:

* Any details about your local setup that might be helpful in troubleshooting.
* Detailed steps to reproduce the bug.

### Improve the documentation 

Noticed a typo on the function help? Think a function could use a better example? Good documentation makes all the difference, so your help to improve it is very welcome!

Functions are described as comments near their code and translated to documentation using [`roxygen2`](https://klutometis.github.io/roxygen/). If you want to improve a function description:

1. Go to `R/` directory in the `r paste0("[code repository](https://github.com/NorwegianVeterinaryInstitute/",NVIpkg, NVIpkg_code,")")`.
2. Look for the file with the name of the function.
3. [Propose a file change](https://help.github.com/articles/editing-files-in-another-user-s-repository/) to update the function documentation in the roxygen comments (starting with `#'`).

### Contribute code 

Care to fix bugs or implement new functionality for our_package? Great! Have a look at the `r paste0("[issue list](https://github.com/NorwegianVeterinaryInstitute/",NVIpkg, "/issues)")` and leave a comment on the things you want to work on. See also the development guidelines below.


## Development guidelines

If you want to contribute code, you are welcome to do so. Please try to adhere 
to some principles and style convention used for `NVIverse`-packages. 

*   Please limit the number of package dependencies for `r NVIpkg_inline`. The use of base 
functions is much appreciated. 

*   New code should generally follow the tidyverse [style guide](http://style.tidyverse.org). 
I recommend to use the [`styler`](https://CRAN.R-project.org/package=styler) 
package to apply spaces: `styler::style_file(filename, scope = "spaces")`. 
Please don't restyle code that has nothing to do with your pull request.

*   You should add a bullet point to `NEWS.md` motivating the change.

*   You should add yourself as a contributor to the `DESCRIPTION`.

*   If you're adding a new function or new arguments to an existing function, you'll also need
    to document them. `NVIverse`-packages use [`roxygen2`](https://cran.r-project.org/package=roxygen2), with
[Markdown syntax](https://cran.r-project.org/web/packages/roxygen2/vignettes/markdown.html),
for documentation. Make sure to re-run `devtools::document()` on the code before submitting. 

*   `NVIverse`-packages use the assert-functions from [`checkmate`](https://CRAN.R-project.org/package=checkmate) package  for argument checking as well as some additional assert_functions in [`NVIcheckmate`](https://github.com/NorwegianVeterinaryInstitute/NVIcheckmate). Adding argument checking for new functions and/or arguments will be highly appreciated.
    
*   If you can, also write a test. `NVIverse`-packages use [`testthat`](https://cran.r-project.org/package=testthat) for tests.

*   Also run `devtools::check()` to make sure your function doesn't imply downstream errors or warnings. 


### Git commit standards
We follow the commit message style guide maintained within the angular.js project.

The start of commit messages should be one of the following:

*   feat: A new feature
*   fix: A bug fix
*   doc: Documentation only changes
*   style: Changes that do not affect the meaning of the code (white-space, formatting, missing semi-colons, etc)
*   refactor: A code change that neither fixes a bug or adds a feature
*   perf: A code change that improves performance
*   test: Adding missing tests
*   chore: Changes to the build process or auxiliary tools and libraries such as documentation generation

Do not capitalize the first letter.


## Code of conduct
Please note that this project is released with a 
[Contributor Code of  Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By participating to this project, you agree to abide by its terms.


## References
This document is adapted from a [template](https://gist.github.com/peterdesmet/e90a1b0dc17af6c12daf6e8b2f044e7c) by @peterdesmet .
