`r NVIpkg_inline`  is available at [GitHub](https://github.com/NorwegianVeterinaryInstitute). 
To install `r NVIpkg_inline` you will need:

- R version > 4.1.0
- R package `remotes`
- Rtools version 4.0, 4.2, 4.3 or 4.4 depending on R version

First install and attach the `remotes` package.  

``` {r, eval = FALSE} 
install.packages("remotes")
library(remotes)
```

To install (or update) the `r NVIpkg_inline` package without vignettes, run the following code:

``` {r install_without, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_without <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = FALSE)', 
              sep = '\n')
cat(install_without, sep="", fill = TRUE)
```

To install (or update) the `r NVIpkg_inline` package with vignettes, you will need to first install some additional R-packages needed to build the vignettes. Check README below in the section [Vignettes](#vignettes) to see which vignettes are available. To install the package with the vignettes, first install the packages: `knitr`, `rmarkdown`, `R.rsp`, and `NVIrpackages` (from GitHub) if they are missing. If you don't use R-studio, you will also need to install Pandoc. Then run the following code:

``` {r install_with, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_with <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = TRUE)', 
              sep = '\n')
cat(install_with, sep="", fill = TRUE)
```
