#### Further documentation
##### Help
The full list of all available functions and datasets can be accessed by typing
``` {r helptext, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
helptext <- paste0('help(package = "', NVIpkg, '")')
cat(helptext, sep="", fill = TRUE)
```

##### Vignettes

Consult the vignettes for task-oriented help.
``` {r vignettetext, message=FALSE, warnings=FALSE, echo = FALSE, prompt = FALSE, comment = ""} 
vignettetext <- paste0('vignette(package = "', NVIpkg, '")')
cat(vignettetext, sep="", fill = TRUE)
```

```{r vignettes, echo = FALSE, prompt = FALSE, comment = ""}
# pkg_vignettes <- NVIpackager::get_vignettes(path = file.path(pkg_path, "vignettes"))
# pkg_vignettes <- paste0("-  ", pkg_vignettes, "  \n")
# pkg_vignettes <- paste0("  \n  \n", paste(pkg_vignettes, collapse = ""), "  \n")
pkg_vignettes <- tools::pkgVignettes(dir = pkg_path)
pkg_vignette_titles <- rep(NA, length(pkg_vignettes$docs)) 

for (i in 1:length(pkg_vignettes$docs)) {
  pkg_vignette_titles[i] <- tools::vignetteInfo(pkg_vignettes$docs[i])$title
  if (grepl("\\.Rmd", pkg_vignettes$docs[i], ignore.case = TRUE)) {
    pkg_vignette_titles[i] <- paste(pkg_vignette_titles[i], "(html)")
    }
  if (grepl("\\.pdf\\.asis", pkg_vignettes$docs[i], ignore.case = TRUE)) {
    pkg_vignette_titles[i] <- paste(pkg_vignette_titles[i], "(pdf)")
  }
}
```

`r if (length(pkg_vignettes > 0)) {paste0("Vignettes in package ", NVIpkg_inline, ":", pkg_vignette_titles)}`

##### NEWS

Please check the [NEWS](`r  paste0("https://github.com/NorwegianVeterinaryInstitute/", NVIpkg, "/blob/main/NEWS")`) for information on new features, bug fixes and other changes.

