`r NVIpkg_inline`  is available in package manager for workbench and at [GitHub](https://github.com/NorwegianVeterinaryInstitute). If needed, you can 
install the development version from the dev-branch at the GitHub repo, see below.

#### Workbench
To install `r NVIpkg_inline` on workbench, run the following code:

``` {r install_workbench, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_workbench <- paste0('install.packages("', NVIpkg, '")')
cat(install_workbench, sep="", fill = TRUE)
```

If you need changes that only are available in the development version, please 
make contact to the developers so that a new release can be published on Workbench. 

#### At personal computer
You may install the package with or without vignettes. Although it will be easier to install without vignettes, it is
recommended to install with vignettes for all `NVIverse` packages except `c("NVIrpackages", "NVIconfig")`.

To install `r NVIpkg_inline` you will need:

- R version > 4.1.0
- R package `remotes`
- Rtools version 4.0, 4.2, 4.3, 4.4 or 4.5 depending on R version

First install and attach the `remotes` package.  

``` {r, eval = FALSE} 
install.packages("remotes")
library(remotes)
```

To install (or update) `r NVIpkg_inline` without vignettes, run the following code:

``` {r install_without, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_without <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = FALSE)', 
              sep = '\n')
cat(install_without, sep="", fill = TRUE)
```

To install (or update) `r NVIpkg_inline` with vignettes, you will need to first install some additional R-packages needed to build the vignettes. Check README below in the section [Vignettes](#vignettes) to see the vignettes that are available. To install the package with the vignettes, first install the packages: `knitr`, `rmarkdown`, `R.rsp`, and `NVIrpackages` (from GitHub) if they are missing. If you don't use R-studio, you will also need to install Pandoc. Then run the following code:

``` {r install_with, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_with <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = TRUE)', 
              sep = '\n')
cat(install_with, sep="", fill = TRUE)
```

To install (or update) the development version (dev-branch) of `r NVIpkg_inline` (with vignettes), run the following code:

``` {r install_dev, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_dev <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    ref = "dev",',
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = TRUE)', 
              sep = '\n')
cat(install_dev, sep="", fill = TRUE)
```

