--- 
title: "README"
output: 
  md_document:
  variant: markdown_github
  
params:
  NVIpkg: "_package_name_"
---

```{r, include = FALSE}
# NVIpkg <- params$NVIpkg
NVIpkg <- stringi::stri_extract_last_words(usethis::proj_path())
NVIpkg_inline <- paste0("`", NVIpkg, "`")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`r paste0(NVIpkg, ": ", desc::desc_get_field(key = "Title"))`
================

<!-- README.md is generated from README.Rmd. Please edit that file -->

  <!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/PetterHopp/NVIdevpkg/branch/master/graph/badge.svg)](https://codecov.io/gh/PetterHopp/NVIdevpkg?branch=master)
  <!-- badges: end -->

  - [Overview](#overview)
  - [Installation](#installation)
  - [Usage](#usage)
  - [Copyright and license](#copyright-and-license)
  - [Contributing](#contributing)

# Overview
`r NVIpkg_inline` provide tools to ...

The package is under development. [Contributions](#contributing) to enhance the package is highly appreciated.  

`r NVIpkg_inline` is part of `NVIverse`, a collection of R-packages with tools to facilitate data management and data reporting at the Norwegian Veterinary Institute (NVI).  

####  Table 1. NVIverse packages
```{r echo = FALSE, resuls = 'asis'}
NVIverse <- as.data.frame(rbind(c("NVIconfig", "Private",
                                  "Configuration information necessary for some NVIverse functions"),
                                c("NVIdb", "Public",
                                  "Tools to facilitate the use of NVI's databases"),
                                c("NVIpretty",  "Public",
                                  "Tools to make R-output pretty in accord with NVI's graphical profile"),
                                c("NVIbatch",  "Public",
                                  "Tools to facilitate the running of R-scripts in batch mode at NVI"),
                                c("NVIcheckmate",  "Public",
                                  "Extension of checkmate with argument checking adapted for NVIverse"),
                                c("OKplan",  "Public",
                                  "Tools to facilitate the planning of surveillance programmes for the NFSA"),
                                c("OKcheck",  "Public",
                                  "Tools to facilitate checking of data from national surveillance programmes")))
colnames(NVIverse) <- c("Package", "Status", "Description")
knitr::kable(x = NVIverse)
```

# Installation
`r NVIpkg_inline`  is available at [GitHub](https://github.com/NorwegianVeterinaryInstitute). 
To install `r NVIpkg_inline` you will need:

- R version > 4.0.0
- R package `devtools`
- Rtools 4.0

First install and attach the `devtools` package.  

``` {r, eval = FALSE} 
install.packages("devtools")
library(devtools)
```

To install (or update) the `r NVIpkg_inline` package, run the following code:

``` {r text, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
text <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '")'), 
	'    upgrade = FALSE,', 
	'    build = TRUE,',
	'    build_manual = TRUE)', sep = '\n')
cat(text, sep="", fill = TRUE)
```

# Usage
To come.

```{r child=system.file('templates', "README_usage.Rmd", package = "NVIpackager")}
```

```{r child=system.file('templates', "README_copyright_and_license.Rmd", package = "NVIpackager")}
```
# Copyright and license

Copyright (c) 2021 Norwegian Veterinary Institute.  
Licensed under the BSD 3-Clause [License](`r  paste0("https://github.com/NorwegianVeterinaryInstitute/", NVIpkg, "/blob/main/LICENSE")` ).
  

```{r child=system.file('templates', "README_contributing.Rmd", package = "NVIpackager")}
```

```{r child=system.file('templates', "README_code_of_conduct.Rmd", package = "NVIpackager")}
```
# Contributing

Contributions to develop `r NVIpkg_inline` is highly appreciated. There are several 
ways you can contribute to this project: ask a question, propose an idea, report 
a bug, improve the documentation, or contribute code. The vignette 
"Contribute to `r NVIpkg`" gives more information.

-----

Please note that the `r NVIpkg` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By 
contributing to this project, you agree to abide by its terms.
