`r NVIpkg_inline`  is available in package manager for workbench and at [GitHub](https://github.com/NorwegianVeterinaryInstitute). 

#### Workbench
To install `r NVIpkg_inline` on workbench, run the following code:

``` {r install_workbench, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_workbench <- paste0('install.packages("', NVIpkg, '")')
cat(install_workbench, sep="", fill = TRUE)
```

#### At personal computer
You may install the package with or without vignettes. Although it will be easier to install without vignettes, it is
recommended to install with vignettes for all packages except `c("NVIrpackages", "NVIconfig")`.

To install `r NVIpkg_inline` you will need:

- R version > 4.1.0
- R package `remotes`
- Rtools version 4.0, 4.2, 4.3 or 4.4 depending on R version

First install and attach the `remotes` package.  

``` {r, eval = FALSE} 
install.packages("remotes")
library(remotes)
```

To install (or update) the `r NVIpkg_inline` package without vignettes, run the following code:

``` {r install_without, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_without <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = FALSE)', 
              sep = '\n')
cat(install_without, sep="", fill = TRUE)
```

To install (or update) the `r NVIpkg_inline` package with vignettes, you will need to first install some additional R-packages needed to build the vignettes. Check README below in the section [Vignettes](#vignettes) to see which vignettes are available. To install the package with the vignettes, first install the packages: `knitr`, `rmarkdown`, `R.rsp`, and `NVIrpackages` (from GitHub) if they are missing. If you don't use R-studio, you will also need to install Pandoc. Then run the following code:

``` {r install_with, message=FALSE, warnings=FALSE, echo=FALSE, prompt = FALSE, comment = ""} 
install_with <- paste(paste0('remotes::install_github("NorwegianVeterinaryInstitute/', NVIpkg, '",'), 
              '    upgrade = FALSE,', 
              '    build = TRUE,', 
              '    build_vignettes = TRUE)', 
              sep = '\n')
cat(install_with, sep="", fill = TRUE)
```
